---
title: "ST558_HW1"
format: html
editor: visual
---

## Being a Data Scientist

  * What do you think being a data scientist is about? 
  I find Data Scientist to be a very broad term, which include wrangling data, performing analysis, modeling data, and communicating data. This requires 
  
  * What differences/similarities do you see between data scientists and statisticians? The primary difference I see between data scientist and statisticians is audience. Data scientist are often business centric while statisticians are more research focus. However, both have the overwhelming goal of understanding the data. A statistician might achieve this by finding a model or distribution to understand the underlying population of the data. A data scientist could work to create a model that uses the data to make immediate or long term decisions.
  
  * How do you view yourself in relation to these two areas?
  The role of a statistician more closely relates to some of the theory knowledge I have studied during my master while data science encompasses a lot of appications of statistics and more.  

## Running Code

```{r}
y <- density(iris$Petal.Width)
class(y) #class of y
typeof(y) #type of y
str(y) #structure of y

```



```{r}
#| echo: false
plot(y$x, y$y, main = "Density of Iris Petal Width", ylab = "Estimated Desnity Values", xlab = "Coordinates")
```

The `echo: false` option is on which prevents the printing of code. The plot shows the estimated density values of the iris petal width.
