---
title: "ST558 HW1"
format: html
editor: visual
---

Ella Gruchacz

## Being a Data Scientist

-   What do you think being a data scientist is about?\
    I find Data Scientist to be a very broad term, which include wrangling data, performing analysis, modeling data, and communicating data. This requires a combination of statistical knowledge, programming practice, and an understanding of the business/domain.

-   What differences/similarities do you see between data scientists and statisticians?\
    The primary difference I see between data scientist and statisticians is audience. Data scientist are often business centric while statisticians are more research focus. However, both have the overwhelming goal of understanding the data. A statistician might achieve this by finding a model or distribution to understand the underlying population of the data. A data scientist could work to create a model that uses the data to make immediate or long term decisions.

-   How do you view yourself in relation to these two areas?\
    The role of a statistician more closely relates to the theory knowledge I have studied during my master; however, it feels very research focus which I consider myself more novice in. Data science relates more closely to the work I did in industry before my master, which included data management and data visualization.

## Running Code

Shows the class, type, and structure of object y, the density of iris petal width.

```{r}
y <- density(iris$Petal.Width)
class(y) #class of y
typeof(y) #type of y
str(y) #structure of y

```

The `echo: false` option is on which prevents the printing of code. The plot shows the estimated density values of the iris petal width.

```{r}
#| echo: false
plot(y$x, y$y, main = "Density of Iris Petal Width", ylab = "Estimated Desnity Values", xlab = "Coordinates")
```
